### 2020-04-24 README.Rmd
Rename project

# archeosciences2019

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2019). Le cru et le cuit : processus post-dépôt et altérations différentielles des matériaux céramiques. *Archéosciences, revue d'Archéométrie*, X, p. X-X. DOI : <https://doi.org/xxx/xxx>.

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2019). *Compendium of R code and data for "Le cru et le cuit : processus post-dépôt et altérations différentielles des matériaux céramiques"*. Accessed YYYY-MM-DD. Online at <https://doi.org/10.5281/zenodo.2613512>.

@@

You can download the compendium as a zip from from this [URL](http://github.com/nfrerebeau/archeosciences2019/archive/master.zip).

Or you can install this compendium as an R package, `archeosciences2019`, from GitHub with:

```{r gh-installation, eval=FALSE}
# install.packages("devtools")
remotes::install_github("nfrerebeau/archeosciences2019")
```

@@

```{sh, eval=FALSE}
git clone https://github.com/nfrerebeau/archeosciences2019.git
```

## Usage
Once the download is complete, open the `archeosciences2019.Rproj` in RStudio to begin working with the package and compendium files.

@@

The original manuscript was produced with R 3.6.0. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages. The `packrat/` directory contains the source code for all the packages we depend on. If all works well, these will be installed on your machine when you open `archeosciences2019.Rproj` in RStudio.

>>>>

# TaphoCeram

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/TaphoCeram.svg)](https://github.com/nfrerebeau/TaphoCeram/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/TaphoCeram.svg?branch=master)](https://travis-ci.org/nfrerebeau/TaphoCeram)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2020). Analyse de données et identification des altérations géochimiques des matériaux céramiques : le cas des productions d'un atelier ibérique (Teruel, Espagne ; IIe-Ier millénaire avant J.-C.). *Archéosciences, revue d'Archéométrie*, X, p. X-X. DOI : <https://doi.org/xxx/xxx>.

@@

> Frerebeau, N., Ben Amara, A. and Cantin, N. (2020). *Compendium of R code and data for "Analyse de données et identification des altérations géochimiques des matériaux céramiques : le cas des productions d’un atelier ibérique (Teruel, Espagne ; IIe-Ier millénaire avant J.-C.)"*. Accessed YYYY-MM-DD. Online at <https://doi.org/10.5281/zenodo.2613512>.

@@

You can download the compendium as a zip from from this [URL](http://github.com/nfrerebeau/TaphoCeram/archive/master.zip).

Or you can install this compendium as an R package, `TaphoCeram`, from GitHub with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("nfrerebeau/TaphoCeram")
```

@@

```{sh, eval=FALSE}
git clone https://github.com/nfrerebeau/TaphoCeram.git
```

## Usage
Once the download is complete, open the `TaphoCeram.Rproj` in RStudio to begin working with the package and compendium files.

@@

The original manuscript was produced with R 3.6.3. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages. The `packrat/` directory contains the source code for all the packages we depend on. If all works well, these will be installed on your machine when you open `TaphoCeram.Rproj` in RStudio.
